---
title: 'Processing Raw Text Assignment'
author: "Atajan Abdyyev"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#do not change this
knitr::opts_chunk$set(echo = TRUE)
```

In each step, you will process your data for common text data issues. Be sure to complete each one in *R* and Python separately - creating a clean text version in each language for comparison at the end. Update the saved clean text at each step, do not simply just print it out. 

## Libraries / R Setup

- In this section, include the libraries you need for the *R* questions.  

```{r}
##r chunk
library(reticulate) # to enable python
library(stringr) # to work on string formatting
library(rvest)
library(tokenizers)
library(stringi)
library(textclean) #contractions
library(hunspell) #spelling
#library(readr)
library(tm)#stemming
library(textstem) # lemmatizing

```

- In this section, include import functions to load the packages you will use for Python.

```{python}
##python chunk
from bs4 import BeautifulSoup
import requests
import re
import nltk
import unicodedata
import contractions
from textblob import Word
import spacy
from nltk.corpus import stopwords
from nltk.stem import PorterStemmer  #stemming
from nltk.stem import LancasterStemmer #stemming

```

## Import data to work with

- Pick a movie that you would interested in analyzing. You can also use **two** one-hour long TV shows or **four** half-hour long TV shows. 
- Search for the subtitles for that movie or TV shows. Please note some of the subtitle websites are junk, do not download anything from a popup! Here is a list of potential sites to use, https://www.nyfa.edu/student-resources/10-great-websites-download-movie-scripts/
- I recommend using this site, https://imsdb.com/
- Find the subtitles for your project.
- List your movie/show here (note that each group should have a different set of subtitles, I will coordinate). If you have picked a TV show, list the specific episodes. 

  - MOVIE/TVSHOW: Shrek
  
- Use EITHER R OR Python to import the text for your movie/tv shows. Be sure to clean out html code at beginning and end of text.

```{r}
##r chunk

```

```{python}
##python chunk
#Movie Chose: SHREK  
#url = https://imsdb.com/scripts/Shrek.html
#Note: commented out code is first version I had to revisit if I were to strip all empty spaces and save as an ongoing bing long text. Updated version has html.parser to keep the format of the subtitles, and updated re.sub() to remove everything before scripts starts and after it ends. New code is shorter and cleaner for subtitles/script task. ALso, python printing without range of [0:xyz] will start outputting mid script, kept from 0 to show it works properly.

blog_post = requests.get("https://imsdb.com/scripts/Shrek.html") #webscrape page
content = blog_post.content #pull the content part of the webscraped page

clean_content = BeautifulSoup(content, 'html.parser') #cleaning the webscraped page via BeautifulSoup package , if adding ,'html-parser' will keep format
clean_text = clean_content.get_text() #get text of the clean content
#clean_text = re.sub('\\n', '', clean_text) #remove \n 
#clean_text = re.sub('\\r', '', clean_text) #remove \r
#clean_text = re.sub('\\t', '', clean_text) #remove \t
#clean_text = re.sub('\\t', '', clean_text) #remove \t
#clean_text = re.sub('\\t', '', clean_text) #remove \t
#clean_text = re.sub('\\s', '', clean_text) #remove \t

#clean_text = re.match("(.*?) END",clean_text).group()# keep everything before THE END
#clean_text = re.sub('^(.*?SCRIPTS)',"", clean_text)#remove everything after first instance of Shrek to hide code section of the page

#clean_text = re.findall('(?<=SCRIPTS ).*$', clean_text)
#clean_text = re.sub('^.*?SHREK',"", clean_text)
clean_text = re.sub(r'^.*?Elliott', '', clean_text, flags=re.DOTALL)#.strip() #VERY IMPORTANT TO KEEP flags!!! cleaning beginnign from additional code junk, everything including first occurance Elliot
clean_text = re.sub(r"(?<=END).*$", '', clean_text,flags=re.DOTALL)#.strip() #VERY IMPORTANT TO KEEP flags!!! cleans everything afther the word END 

                                  
print(clean_text[0:200])
```


Save results as a .txt file for later assignments using either R OR Python.

```{r}
##r chunk
#write(clean_text, 'clean_text_r.txt')
```

```{python}
##python chunk 
with open('clean_text_Shrek.txt', 'w') as outfile:
  outfile.write(str(clean_text)) #save the cleaned text file 
```

## Lower case

- Lower case the text you created using *R*.

```{r}
##r chunk
library(reticulate)
colnames(py$clean_text)
clean_text_r = str_to_lower(py$clean_text) #lowercasing with r
print(unlist(strsplit(clean_text_r, "\r"))[6:10])


```

- Lower case the text you created using python.

```{python}
##python chunk
clean_text = clean_text.lower() #lower cased text and save as clean text

print(clean_text[1:200]) #output first 2000 chars
```

## Removing symbols

- Use the `stringi` package to remove any symbols from your text. 

```{r}
##r chunk
library(reticulate)

clean_text_r = stri_trans_general(str = clean_text_r,
                   id = "latin-ascii") # remove any symbols

#head(clean_text_r,10)
print(unlist(strsplit(clean_text_r, "\r"))[6:20])

```

- Use the `unicodedata` in python to remove any symbols from your text. 

```{python}
##python chunk


def remove_accented_chars(text):
  text = unicodedata.normalize('NFKD', text).encode('ascii', 'ignore').decode('utf-8', 'ignore')
  return text

clean_text =remove_accented_chars(clean_text) #remove any sumbols with python
print(clean_text[0:350])
```

## Contractions

- Replace all the contractions in your webpage using *R*.

```{r}
##r chunk
clean_text_r = str_replace_all(clean_text_r, 
                        pattern = "’", 
                        replacement = "'")

clean_text_r = replace_contraction(clean_text_r, 
                    contraction.key = lexicon::key_contractions, #default
                    ignore.case = T) #default
print(unlist(strsplit(clean_text_r, "\r"))[6:20])

```

- Replace all the contractions in your webpage using python.

```{python}
##python chunk


clean_text=contractions.fix(clean_text) #replacing contractions
print(clean_text[0:350])  #output text wtithout contractions



```
  
## Tokenization 

- Use the `tokenize_words` function to create a set of words for your *R* clean text. 

```{r}
##r chunk
tokenized_r = tokenize_words(clean_text_r,
               lowercase = T,
               stopwords = NULL, #more on this later
               strip_punct = T,
               strip_numeric = F,
               simplify = F) #list format
tokenized_r[[1]][1:20] #saved tokenized words
```

- Use `nltk` or `spacy` to tokenize the words from your python clean text. 

```{python}
##python chunk
tokenized_py = nltk.word_tokenize(clean_text) #tokenize words
print(tokenized_py[0:20])
```

## Spelling

- Fix any spelling errors with the `hunspell` package in *R* - it's ok to use the first, most probable option, like we did in class. 
- DO NOT save results from this step!


```{r}
##r chunk
tokenized_r_vector =as.vector(tokenized_r[[1]]) # vectorized tokenized words  just in case

# Spell check the words
spelling.errors <- hunspell(tokenized_r_vector)
spelling.sugg <- hunspell_suggest(unique(unlist(spelling.errors)), dict = dictionary("en_US"))

# Pick the first suggestion
spelling.sugg <- unlist(lapply(spelling.sugg, function(x) x[1]))
spelling.dict <- as.data.frame(cbind(spelling.errors = unique(unlist(spelling.errors)),spelling.sugg))
spelling.dict$spelling.pattern <- paste0("\\b", spelling.dict$spelling.errors, "\\b")

#Replace the words 
stri_replace_all_regex(str = tokenized_r_vector,
                       pattern = spelling.dict$spelling.pattern,
                       replacement = spelling.dict$spelling.sugg,
                       vectorize_all = FALSE)[1:20]
```

- Fix your spelling errors using `textblob` from python. 

```{python}
##python chunk
#wordlist = words#["thse", "wods", "mispelled"]

#you must give it a tokenized list 
#if you give it a long string, you'll get single letters back
#[Word(token).correct() for token in words]
[Word(token).correct() for token in tokenized_py][0:20] #corrected tokens using the tokenized list I made in previous task
```

## Lemmatization

- Lemmatize your data in *R* using `textstem`. 

```{r}
##r chunk
lemmatized_r_words = lemmatize_words(tokenized_r_vector) #lemmatized words
lemmatized_r_sentences = lemmatize_strings(clean_text_r) #lemmatized sentences 
#lemmatized_r_words
#lemmatized_r_sentences

print(unlist(strsplit(lemmatized_r_sentences, " "))[1:10])
print(lemmatized_r_words[1:10])

```

- Lemmatize your data in python using `spacy`. 

```{python}
##python chunk
nlp = spacy.load('en_core_web_sm')

def lemmatize_text(text):
  text = nlp(text)
  text = " ".join([word.lemma_ if word.lemma_ != "-PRON-" else word.text for word in text])
  return text

lemmatized_py_sentences = lemmatize_text(clean_text) #lemmatized sentence
print(lemmatized_py_sentences[1:250])
lemmatized_py_words = nltk.word_tokenize(lemmatized_py_sentences) #tokenize words and lemmatized words
print(lemmatized_py_words[1:50])
```

## Stopwords

- Remove all the stopwords from your *R* clean text. 

```{r}
##r chunk
clean_text_r_removed = removeWords(clean_text_r, stopwords(kind = "SMART")) # removing stop words
clean_text_r_removed = tokenize_words(clean_text_r_removed,
               lowercase = T,
               stopwords = NULL, #more on this later
               strip_punct = T,
               strip_numeric = F,
               simplify = F) #list format
clean_text_r_removed[[1]][1:15]
```

- Remove all the stop words from your python clean text. 

```{python}
##python chunk


set(stopwords.words('english'))
clean_text_removed=[word for word in nltk.word_tokenize(clean_text) if word not in stopwords.words('english')] #removed stopwords
clean_text_removed[0:25]
```

## Check out the results

- Print out the first 100 tokens of your clean text from *R*. 

```{r}
##r chunk 
clean_text_r_removed[[1]][1:100] #prinitng first 100 tokens from the list
```

- Print out the first 100 tokens of your clean text from python. 

```{python}
##python chunk
print(clean_text_removed[0:100])#prinitng first 100 tokens from the list
```

Note: here you can print out, summarize, or otherwise view your text in anyway you want. 

# Save the Results for Future Assignments

- Using either R or Python save the cleaned text to a .txt file to use in future assignments.

```{r}
##r chunk
#write(clean_text, 'clean_text_r.txt')
```

```{python}
##python chunk
with open('cleaned_text_Shrek_final.txt', 'w') as outfile:
  outfile.write(str(clean_text)) #save the file
```


- QUESTION: Compare the results from your processing. Write a short paragraph answering the following questions. You will need to write more than a few sentences for credit. 
  - Which text appears to be "cleaner"? 
  
  
  - Or are they the same? 
  
  - What differences can you spot? 
  
  - Which processing approach appears to be easier? 

- ANSWER:
Second file seems to be a better and cleaner result. Also, R seems to do a better job lemmatizing and cleaning stop words than python. 

I noticed & symbol got in python after stop words than in R. Also textblob in Python correcting spelling considered Shrek as Shriek while R kept it as Shrek. As for lemmatizing, order in R was not altered than Python, makes it easier to quickly glance values in the right order in R than in Python.R and Python are not a lot different but I would go with R here for lemmatizing and stop words. Otherwise Cleaned text is generally same as R, difference isnt drastic but I would trust with contractions, lemmatizing, and stopwords to R more.Only when doing lemmatizing and tokenizing words, R seems to do a better job.
Overall, Python was easier because I could us re package to remove all the code part of webscraped page easily, also slicing is easier than R and requires less work in general to clean data at all stages.